---
title: "Client Report"
output: 
      pdf_document
author: IBH
params:
  dep_var: NA
  focus_data: NA
  file_data: NA
  arima_summary: NA
  explanation_tb: NA
header-includes:
      - \usepackage{xcolor}
      - \definecolor{mybgcolor}{HTML}{F9F9F9}
      - \usepackage{sectsty}
      - \allsectionsfont{\color{red}}
classoption:
      - twocolumn
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

\pagecolor{mybgcolor}
\color{black}

:::::::::: {.columns}

::: {.column width=50%}

## Change in `r params$dep_var`

**This graph shows how much the person has changed in `r params$dep_var` over time.**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.height=3}
ggplot(params$focus_data, aes_string(x = "Time", y = params$dep_var)) +
      geom_point(size = 1.5) +
      geom_point(data = params$focus_data[(params$focus_data[,3] == min(params$focus_data[,3], na.rm = T)), ], color="#87bc45", 
                 size=4) +
      geom_point(data = params$focus_data[(params$focus_data[,3] == max(params$focus_data[,3], na.rm = T)), ], color="orange", 
                 size=4) +
      geom_smooth() +
      scale_color_brewer(palette = "Set1") +
  theme_minimal() +
  theme(plot.background = element_rect(colour = "#909090", fill=NA, size=2))
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
TimeSeriesData <- na_interpolation(params$focus_data[,3]) 
notrend_test <- notrend_test(TimeSeriesData)
anytrend_test <- notrend_test(TimeSeriesData, test = "MK",
                                 factor.length = "adaptive.selection")
variance_box_test <- Box.test(TimeSeriesData, type = "Box-Pierce", lag = 1)
if ( notrend_test$p.value < 0.05 |
         anytrend_test$p.value < 0.05 |
         variance_box_test$p.value < 0.05) {
      out = "Well-being changed significantly over this time period."
} else {
      out = "Well-being did not change significantly over this time period."
}
```

`r out`

```{r, echo=FALSE, message=FALSE, warning=FALSE}

min_time <- params$focus_data[params$focus_data[,3] == min(params$focus_data[,3], na.rm = T), 2]
min_time <- min_time[!is.na(min_time)]
max_time <- params$focus_data[params$focus_data[,3] == max(params$focus_data[,3], na.rm = T), 2]
max_time <- max_time[!is.na(max_time)]

min_var_string <- paste0(min_time, collapse = ", ")
max_var_string <- paste0(max_time, collapse = ", ")

```

## Key correlates of well-being 

**This graph shows the key correlates of well-being from a linear analysis.**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=14, fig.height=9}
max_x = 0.5
min_x = -0.5
  
if (max(params$arima_summary$Coef) > max_x) {
    max_x = max(params$arima_summary$Coef)
}
if (min(params$arima_summary$Coef) < min_x) {
    min_x = min(params$arima_summary$Coef)
}

params$arima_summary %>%
    mutate(decision = case_when(
      errcol == "Yes" ~ "Important",
      errcol == "No" ~ "Not significantly important"),
      decision = factor(decision, 
                        levels = c("Important", "Not significantly important")),
      xmin = Coef - 2*SE, 
      xmax = Coef + 2*SE,
    ) %>%
    ggplot(aes(x = Coef,
               y = reorder(variable, Coef), # ordering the bars from high to low by the value of meanImp
               fill = decision,
               text = paste("Decision:", decision,
                            "\nCoef:",round(Coef, 3)))) + # the text argument is specific for the tooltip in plotly
    geom_col() +
    # manually changing color for each decision
    scale_fill_manual(values = c("Important" = "#87bc45",
                                 "Not significantly important" = "grey")) +
    # giving labels to x axis, y axis and legend (fill)
  labs(x = paste0("< more this way, less ", dep_var, " | more this way, more ", dep_var, " >"), 
         y = " ", fill = " ") +
    xlim(min_x, max_x) +
    # using minimal theme
    theme_minimal() +
      theme(plot.background = element_rect(colour = "#909090", fill=NA, size=4),
            text = element_text(size = 20),
            #axis.title.x = element_text(size = 20),
            legend.position = "none")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
out_linear1 <- get_linear_analysis_summary(params$arima_summary) 

out_linear2 <- paste0("Processes in grey are generally less important to your well-being than processes in green. ",
           "Processes on the right increase the ", colnames(params$focus_data)[3], 
           ". Processes on the left decrease the ", colnames(params$focus_data)[3], ". ",
           linear_imp_report(params$arima_summary, params$focus_data))
```


`r out_linear1`  
  
\begingroup
\fontsize{8}{8}\selectfont
`r out_linear2`
\endgroup

:::

::: {.column width=50%}

## Determinants of well-being: How this person compares to the average

**This plot presents how much the person engages in different behaviors, compared to the average.**

```{r, echo=FALSE, message=FALSE, warning=FALSE}

stats <- get_variable_stat(params$focus_data, params$file_data)

summary_data <- stats %>%
    mutate(ind_perc = as.numeric(X..mean)-20) %>%
      dplyr::select(Variable, ind_perc) %>% 
      spread(Variable, ind_perc) %>%
      rbind(rep(100, ncol(.)),rep(0, ncol(.))) %>%
      slice(2:3, 1)

min_percentile = min(stats$X..mean)
max_percentile = max(stats$X..mean)
min_perc_var = stats %>%
      filter(X..mean == min(X..mean)) %>%
      dplyr::select(Variable)
max_perc_var = stats %>%
      filter(X..mean == max(X..mean)) %>%
      dplyr::select(Variable)


max_exp <- params$explanation_tb %>%
      filter(Variablename == as.character(max_perc_var)) %>%
      dplyr::select(Explanation)

min_exp <- params$explanation_tb %>%
      filter(Variablename == as.character(min_perc_var)) %>%
      dplyr::select(Explanation)

sp_1 <- paste0("This person is in the ",
                 round(max_percentile, 0),
                 "th percentile for ",
                 max_perc_var,
                 ". ",
                 max_perc_var,
                 " means ",
                 max_exp, 
                 ". This means this person does this more than ",
                 round(max_percentile, 0),
                 " percent of people.\n\n")
    
sp_2 = paste0("This person is in the ",
                 round(min_percentile, 0),
                 "th percentile for ",
                 min_perc_var,
                 ". ",
                 min_perc_var,
                 " means ",
                 min_exp, 
                 ". This means this person does this less than ",
                 round(100-min_percentile, 0),
                 " percent of people.")
```
       
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=10}
fmsb::radarchart( summary_data  , axistype=1 , 
    #custom polygon
    pcol=rgb(0.34,0.60,0.18,0.9) , pfcol=rgb(0.34,0.48,0.18,0.5) , plwd=5 , 
    #custom the grid
    cglcol="grey", cglty=1, axislabcol="grey", caxislabels=seq(20,100,20), cglwd=1,
    #custom labels
    vlcex=1.5 
    )
box(col = "#5d5d5d",
      which = "plot",
      lwd = 2)
```

\begingroup
\fontsize{8}{8}\selectfont
`r sp_1`  
\endgroup

\begingroup
\fontsize{8}{8}\selectfont
`r sp_2`  
\endgroup

## Potential targets of change 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
targets <- target_of_change(params$arima_summary)
```

`r targets`

:::

::::::::::

